---
title: "R Notebook"
output: html_notebook
---

# PART II - IMPROVED MODEL - Xgboost

### Step 0: specify directories.

Set the working directory to the image folder. Specify the training and the testing set. For data without an independent test/validation set, you need to create your own testing data by random subsampling. In order to obain reproducible results, set.seed() whenever randomization is used. 

```{r wkdir improved xgb, eval=FALSE}
set.seed(2019)
path <- "~/Desktop/GR5243 Applied Data Science/Project 3/Spring2019-Proj3-spring2019-proj3-grp5"
setwd(path)
```

Provide directories for training images. Low-resolution (LR) image set and High-resolution (HR) image set will be in different subfolders. 
```{r}
train_dir <- "../data/train_set/" # This will be modified for different data sets.
train_LR_dir <- paste(train_dir, "LR/", sep="")
train_HR_dir <- paste(train_dir, "HR/", sep="")
train_label_path <- paste(train_dir, "label.csv", sep="") 


train_dir <- "/data/train_set/" # This will be modified for different data sets.
train_LR_dir <- paste(path,train_dir, "LR/", sep="")
train_HR_dir <- paste(path,train_dir, "HR/", sep="")
train_label_path <- paste(path,train_dir, "label.csv", sep="") 

length(list.files(train_LR_dir))
length(list.files(train_HR_dir))
```

### Step 1: set up controls for evaluation experiments.

In this chunk, we have a set of controls for the evaluation experiments. 

+ (T/F) cross-validation on the training set
+ (number) K, the number of CV folds
+ (T/F) process features for training set
+ (T/F) run evaluation on an independent test set
+ (T/F) process features for test set

```{r exp_setup improved xgb}
run.cv=TRUE # run cross-validation on the training set
K <- 5  # number of CV folds
run.feature.train=TRUE # process features for training set
run.test=TRUE # run evaluation on an independent test set
run.feature.test=TRUE # process features for test set
```

Using cross-validation or independent test set evaluation, we compare the performance of models with different specifications. In this example, we use GBM with different `depth`. In the following chunk, we list, in a vector, setups (in this case, `depth`) corresponding to models that we will compare. In your project, you might compare very different classifiers. You can assign them numerical IDs and labels specific to your project. 

```{r model_setup improved xgb}
model_values <- c(270,285,300) ### Tuning values
model_labels = paste("XG Boosting with nrounds =", model_values)
```

### Step 2: import training images class labels.

We provide extra information of image label: car (0), flower (1), market (2). These labels are not necessary for your model.

```{r train_label improved xgb}
extra_label <- read.csv(train_label_path, colClasses=c("NULL", NA, NA))
```

### Step 3: construct features and responses

`feature.R` should be the wrapper for all your feature engineering functions and options. The function `feature( )` should have options that correspond to different scenarios for your project and produces an R object that contains features and responses that are required by all the models you are going to evaluate later. 
+ `feature.R`
  + Input: a path for low-resolution images.
  + Input: a path for high-resolution images.
  + Output: an RData file that contains extracted features and corresponding responses

```{r feature improved xgb}
source("../XGB/lib/feature.R")

tm_feature_train <- NA
if(run.feature.train){
  tm_feature_train <- system.time(dat_train <- feature(train_LR_dir,train_HR_dir))
  feat_train <- dat_train$feature
  label_train <- dat_train$label
  }

tm_feature_train

save(dat_train, file="../XGB/output/feature_train.RData")
load("../XGB/output/feature_train.RData")
```


### Step 4: Train a classification model with training images

Call the train model and test model from library. 

`train.R` and `test.R` should be wrappers for all your model training steps and your classification/prediction steps. 
+ `train.R`
  + Input: a path that points to the training set features and responses.
  + Output: an RData file that contains trained classifiers in the forms of R objects: models/settings/links to external trained configurations.
+ `test.R`
  + Input: a path that points to the test set features.
  + Input: an R object that contains a trained classifier.
  + Output: an R object of response predictions on the test set. If there are multiple classifiers under evaluation, there should be multiple sets of label predictions. 
```{r loadlib improved xgb}
source("../XGB/lib/train.R")
source("../XGB/lib/test.R")
```

#### Model selection with cross-validation

* Do model selection by choosing among different values of training model parameters, that is, the interaction depth for GBM in this example. 
```{r runcv improved xgb, message=FALSE, warning=FALSE}
source("../XGB/lib/cross_validation.R")
if(run.cv){
  err_cv_xgboost <- array(dim=c(length(model_values), 2))
  for(k in 1:length(model_values)){
    cat("Values=", k, "\n")
    err_cv_xgboost[k,] <- cv.function(feat_train, label_train, model_values[k],K)
  }
  save(err_cv_xgboost, file="../XGB/output/err_cv_xgboost.RData")
}
err_cv_xgboost
```


#### Visualize cross-validation results. 

```{r cv_vis improved xgb}
if(run.cv){
  
  load("../XGB/output/err_cv_xgboost.RData")
  
  plot(model_values, err_cv_xgboost[,1], xlab="Interaction Depth", ylab="CV Error",
       main="Cross Validation Error", type="n", 
       ylim=c(min(err_cv_xgboost[,1])-max(sd(err_cv_xgboost[,2]))-0.03, max(err_cv_xgboost[,1])+max(sd(err_cv_xgboost[,2]))+0.03)
       )
  points(model_values, err_cv_xgboost[,1], col="blue", pch=16)
  lines(model_values, err_cv_xgboost[,1], col="blue")
  arrows(model_values, err_cv_xgboost[,1]-err_cv_xgboost[,2], model_values, err_cv_xgboost[,1]+err_cv_xgboost[,2], 
        length=0.1, angle=90, code=3)
}
# Average cv error and cv SD
apply(err_cv_xgboost, 2, mean)
```


* Choose the "best"" parameter value
```{r best_model improved xgb}
model_best=model_values[1]
if(run.cv){
  model_best <- model_values[which.min(err_cv_xgboost[,1])]
}
par_best <- list(nr=model_best) #285
```

* Train the model with the entire training set using the selected model (model parameter) via cross-validation.
```{r final_train improved xgb}
tm_train=NA
tm_train <- system.time(fit_train <- train(feat_train, label_train,par_best))
save(fit_train, file="../XGB/output/fit_train_xgboost.RData")
```

### Step 5: Super-resolution for test images

Feed the final training model with the completely holdout testing data. 
+ `superResolution.R`
  + Input: a path that points to the folder of low-resolution test images.
  + Input: a path that points to the folder (empty) of high-resolution test images.
  + Input: an R object that contains tuned predictors.
  + Output: construct high-resolution versions for each low-resolution test image.
  
```{r superresolution improved xgb}
source("../XGB/lib/superResolution.R")

test_dir <- "../data/test_set/" # This will be modified for different data sets.
test_LR_dir <- paste(test_dir, "LR/", sep="")  # read LR images
test_HR_dir <- paste(test_dir, "HR/", sep="")  # store resoluted images
length(list.files(test_LR_dir))
#all.img = 
#test.img = all.img[sample(50:length(all.img), size = 5, replace = F)]

tm_test=NA
if(run.test){
  load(file="../XGB/output/fit_train_xgboost.RData")
    tm_test.2 <- system.time(superResolution_xgboost2(test_LR_dir, test_HR_dir, fit_train))
}
```

### Summarize Running Time

Prediction performance matters, so does the running times for constructing features and for training the model, especially when the computation resource is limited. 
```{r running_time improved xgb}
cat("Time for constructing training features=", tm_feature_train[1], "s \n")
#cat("Time for constructing testing features=", tm_feature_test[1], "s \n")
cat("Time for training model=", tm_train[1], "s \n")
cat("Time for super-resolution=", tm_test[1], "s \n")